Macro Impacts

### 2016-07-17 Macro Impacts Revised.tex
Updating Stuff

%\pagebreak
%Meeting Agenda: Found bounds for $\Xi$. We need to map intensity to the surface - how? Do we make a generous over estimate again? If so, how should we approach it?
\end{document}

>>>>

\section{Realistic Model}
Since I have realized that the curving of rays is non-negligible, Professor Tolley has suggested doing a realistic treatment of the problem. The displacement potential satisfies the inhomogeneous wave equation
-\f{f}{\rho}&=v(r)^2\nabla^2\phi-\partial_t^2\phi\,,
where $v(r)=a^2-b^2r^2$. Note, $b^2$ is several orders of magnitude smaller than $a^2$, so that the background varies slowly with respect to the frequency of the waves so the WKB approximation is appropriate. Denote 
\hat L=\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)-(l(l+1))}+\omega^2\,,
It is easy to see that $\hat L$ is Hermitian since it can be put in Sturm--Liouville form when stated as an eigenvalue problem
-\f{v(r)^2}{r^2}\ps{\partial_r(r^2\partial_r)+\p{\f{r^2}{v(r)^2}\omega^2-l(l+1)}}\phi=\lambda\phi\,.
Or, in another rearrangement:
&\ps{\partial_r(r^2\partial_r)+\p{\lambda\f{r^2}{v(r)^2}+\ps{\f{r^2}{v(r)^2}\omega^2-l(l+1)}}}\phi=0\,,\\
&(s(r)\phi'(r))'+\p{\lambda\rho(r)-q(r)}\phi(r)=0\,.
where
s(r)&=r^2\,,\\
\rho(r)&=\f{r^2}{v(r)^2}\,,\\
q(r)&=\f{r^2}{v(r)^2}\omega^2-l(l+1)\,.
$\rho$ is known as the weight function. To satisfy the Sturm--Liouville theorem, $s,\rho,q$ must be continuous on the interval $[0,\f ab]$, and $s,\rho$ positive-valued on $(0,\f ab)$. Clearly this is indeed the case. Two solutions $\phi_1$ and $\phi_2$ are orthogonal with respect to the Sturm--Liouville equation if
\int_0^{\f ab}\diff r\rho(r)\phi_1(r)\phi_2(r)=0\,.
Two eigenfunctions $\phi_1$ and $\phi_2$ are orthogonal if the boundary conditions satisfy
s(r)(\phi_1(r)\phi_2'(r)-\phi_1'(r)\phi_2(r))\vert_0^{\f ab}=0\,.
Since $s(0)=0$, we must only be concerned with the behavior of $\phi$ at $\f ab$. A brief check will verify that the eigenvectors go to 0 at $\f ab$ hence the our solutions are orthogonal with respect to $\rho$. Note that $s(0)\rho(0)=0$ hence the equation is singular, and our eigenvalues may be complex.
\delta(\lambda-\lambda')=\int_0^{\f ab}\diff r\rho(r)\phi_{\lambda}(r)\phi_{\lambda'}(r)\,,
hence, since any function can be decomposed in terms of these eigenfunctions
\delta(r-r')&=\int\diff\lambda f_{\lambda}\phi_{\lambda}(r)\,,\\
\int\diff r\rho(r) \phi_{\lambda'}(r)\delta(r-r')&=\int\diff r \rho(r)\phi_{\lambda'}(r)\int\diff\lambda f_{\lambda}\phi_{\lambda}(r)\,,\\
\rho(r')\phi_{\lambda'}(r')&=\int\diff\lambda f_\lambda\int\diff r\rho(r)\phi_{\lambda}(r)\phi_{\lambda'}(r)\,,\\
\rho(r')\phi_{\lambda'}(r')&=\int\diff\lambda f_\lambda\delta(\lambda-\lambda')\,,\\
\rho(r')\phi_{\lambda'}(r')&=f_{\lambda'}\,,\\
Hence
\delta(r-r')=\int\diff\lambda\rho(r')\phi_\lambda(r')\phi_\lambda(r)\,.
Call
u=\f{\sqrt{a^2b^2-\lambda-\omega^2}}{2ab}\,.
The exact solution to the eigenvalue problem is
\f{v(r)^{\f{1+u}{2}}}{ab^2 r^{l+1}}\p{a C_1 2\te{F}1\ps{\f12u-1,\f12(1+u),\f12-l,\p{\f{b}{a}r}^2}+\I br\p{-\f{b}{a}r}^{2l} C_22\te{F}1\ps{1+l+\f12 u,\f12(1+u),\f32+l,\p{\f ba r}^2}}\,.
Regularity at the origin fixes $C_1=0$. The solution is then
\phi_\lambda(r)=\I C\f{b^{2l-1}}{a^{2l+1}}r^lv(r)^{\f{1+u}{2}}\p{\,2\te{F}1\ps{1+l+\f12 u,\f12(1+u),\f32+l,\p{\f ba r}^2}}\,.
We now employ the WKB ansatz (where $\delta\ll \f{a^2}{b^2R_E^2}$ *this is a guess - think about it!)
\phi_\lambda(r)=\exp\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}(r)}\,,
and hence (note that $\delta$ is just an auxiliary variable that we will absorb into $S$ at the end of the calculation)
\partial_r \phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}\phi_\lambda(r)\,,\\
&\sim\f1\delta S_{\lambda0}'(r)\phi_\lambda(r)\,,\\
\partial_r^2\phi_\lambda(r)&=\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}''(r)}\phi_\lambda(r)+\p{\f1\delta\sum_{n=0}^{\infty}\delta^nS_{\lambda n}'(r)}^2\phi_\lambda(r)\,,\\
&\sim\f1\delta S_{\lambda0}''(r)\phi_\lambda(r)+\f1{\delta^2}S_{\lambda0}'^2(r)\phi_\lambda(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)\phi_\lambda(r)\,.
Thus
r^2\p{\f1\delta S_{\lambda0}''(r)+\f1{\delta^2}S_{\lambda0}'^2(r)+\f{2}{\delta}S_{\lambda0}'(r)S_{\lambda1}'(r)}+2r\f1\delta S_{\lambda0}'(r)=-\p{\f{r^2}{v(r)^2}(\lambda+\omega^2)-l(l+1)}\,.
As we take $\delta$ to zero, the dominant balance is
S'_{\lambda 0}(r)=\I\delta\sqrt{\p{\f{(\lambda+\omega^2)}{v(r)^2}-\f{l(l+1)}{r^2}}}\,,
The first order contribution is then determined by
S_{\lambda1}'(r)=-\f{1}{r}-\f{S_{\lambda0}''(r)}{2S_{\lambda0}'(r)}\,.
The WKB Approximation may not be necessary given that we have a relatively easy-to-write exact solution in terms of the hypergeometric 2F1 function. Moreover, we are not interested in the particle-like behavior of the waves - we are only interested in the energy density on a surface. Now, supposing we've properly normalized $\phi_\lambda$, we have the Green's function
G(r,r')=\int_{-\infty}^{\infty}\diff\omega\sum_{l=1}^{\infty}\sum_{m=-l}^l\int\diff\lambda\rho(r')\f{\bar \phi_{\lambda}(r)\phi_{\lambda}(r')}{\lambda+\I\epsilon}Y_{lm}(\theta,\phi)e^{\I m\phi}e^{\I\omega t}\,.
In order to find $\mu$, 
Now, we wish to consider the source proportional to $\delta(z-v_X t)=\delta(\theta)\delta(\phi)\delta(r-v_X t)$. The solution is then
\int_V\diff V'\int_{-\infty}^{\infty}\diff t' G(r,r')\delta(r'-v_X t')
\end{document}
